Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts

### 2019-06-26 paper/Draft.tex
Done with discussions of the IR plots replicating.

For a direct comparison of my results and \cite{coibion2012can}, I first explore the impulse responses along one-standard-deviation confidence band of inflation $y_{t+k}$, and SPF forecast errors $\overline {FE}_{t+h|t+k}$ to one standard deviation of each shock at time $t$, and SPF disagreements $\overline Disg_{t+h|t+k}$ and average uncertainty $\bar\sigma^2_{t+h|t+k}$ to the absolute value of shocks. The sample period is the same to that in Figure 2 from \cite{coibion2012can}: 1987-2007. The only difference is that CPI and PCE inflation are used instead of GDP deflator as in their paper.

@@

Standard errors are computed using the parametric bootstrapping approach as in \cite{coibion2012can} paper.

@@

Both SE and NI models predict disagreements rise after a shock and gradully converge to zero over the long-run.

>>>>

For a direct comparison of my results and \cite{coibion2012can}, I first explore the impulse responses along one-standard-deviation confidence band of inflation $y_{t+k}$, and SPF forecast errors $\overline {FE}_{t+h|t+k}$ to one standard deviation of each shock at time $t$, and SPF disagreements $\overline Disg_{t+h|t+k}$ and average uncertainty $\bar\sigma^2_{t+h|t+k}$ to the absolute value of shocks. The sample period is the same to that in Figure 2 from \cite{coibion2012can}: 1987-2007. The only difference is that CPI and PCE inflation are used instead of GDP deflator as in their paper. Besides, standard errors are computed using the parametric bootstrapping approach as in \cite{coibion2012can}.

@@

@@

FIRE predicts zero disagreements while both SE and NI models imply disagreements pick up following shocks regardless of the sign and gradully drop over longer horizon.  Looking into the graph, the average response of disgreements to the absolute value of technology and oil shocks does exhibite a pattern similar to the later.  Note now that the initial response is not statistically significant(same as the original result.). Besides, there is also one subtle difference between the SE and NI on disagreements in that disagreements always exist with the presense of private signals, in contrast, SE predicts that the disagreements is zero over the long run. The evidence from impulse response of disagreements seem to be more consistent with SE than NI.
